Reading Notes

### 2020-08-05 2pd.tex
replaced all missing citations

\section*{Motivation}
<why do opvs matter>
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

@@

\subsection*{Organic Photovoltaics}
<history>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was tang1986<cite> used a bilyaer structure
Saricifti and Heeger 1992 <cite> discovered BHJ
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. <cite>
non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

@@

Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
The resolution of coarse grain systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
Other goarse-graining schemes may group functional groups together <cite> or even represent an entire amino acid with a single site <cite>.
General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014} 
A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition.\cite{Shelley2001}
Which model is right depends on the length and time scale on which the property of interest can be observed.

For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)<cite> -- it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily--a process called backmapping.
In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
<what stands in our way?>

@@

<Talk about what exists and why it is not enough>
<votca, Peng2019a> 
Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
It also allows for charge transport calculations using KMC similar to MorphCT <cite>

>>>>

\section*{Motivation}
<why do opvs matter>
<the climate is in crisis, energy consumption of fossil fuels strongly increases CO2 output which affects our climate>\cite{Solomon2009a}
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

@@

\subsection*{Organic Photovoltaics}
<history>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was \cite{Tang1986b} used a bilyaer structure
Saricifti and Heeger 1992 \cite{Saricifti1992} used polymer:fullerene mixture.
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. \cite{Yu1995}
non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

@@

Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers. Even if the simulation was to complete, there would be too much information to process accurately. CGing allows scientists to FOCUS their experiments.\cite{Baschnagel2000}
The resolution of coarse grain systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
Other coarse-graining schemes may group functional groups together \cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019a}.

General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014} 
A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition.\cite{Shelley2001}
Which model is right depends on the length and time scale on which the property of interest can be observed.

For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)\cite{Huang2010} -- it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily--a process called backmapping.
In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
<what stands in our way?>

@@

<Talk about what exists and why it is not enough>
<votca, Peng2019a> 
Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
It also allows for charge transport calculations using KMC similar to MorphCT \cite{Lukyanov2010}
